### 2012-02-16 abs.tex
Restructured into smaller files, wrote much of chapter 2.

This dissertation considers two types of ``gaps'' in the lexicon. In both cases, it is argued that current generative models can be modified minimally to account for the apparent overgeneration of gapped structures. The first part of the dissertation considers the underlying phonological structure of morphs, specifically medial consonant clusters in English. A number of prior studies have argued that the grammar must have a separate ``phonotactic'' module to account

at the level of prosodic word. In both cases, it is argued that the i

>>>>

This dissertation uses the status of unattested words to provide evidence for the architecture of Universal Grammar (UG).

The first part of the dissertation considers constraints on phonological underlying representations (URs). 
It is proposed that UG countenances no language-specific constraints on URs. 
Putative counterexamples are dismissed as either diachronic contingencies or as induced by synchronic constraints not coterminous with the morph.
A corpus study of the inventory of medial consonant clusters in English simplex words reveals that a number of gaps in this system are accidental in nature, and do not require the structural explanations proposed in prior studies. 
A reanalysis of a study of Turkish wordlikeness judgements reveals that speakers are sensitive to constraints on underlying representations if and only if they are induced by phonological alternations.
A systematic review of English wordlikeness studies reveals once the presence or absence of gross phonotactic violations is controlled for, current gradient phonotactic models are superfluous.

The second part investigates inflectional gaps, complex words judged ineffable.
It is proposed that UG countenances no language-specific constraints on phonological output representations which give rise to ineffability. 
Putative counterexamples are dismissed.
%This indicates that Universal Grammar does not incorporate any inviolable constraints on surface structure. 
It is proven that a model of inviolable constraint learning fails to converge on the proper grammar. 
Models which store complex words are shown to result in extensive undergeneration. 
An analysis of inflectional gaps as reflexes of unproductive morphophonological generalizations is put forth and applied to cases from English, Spanish, Greek, and Russian.

### 2012-02-16 ack.tex
Restructured into smaller files, wrote much of chapter 2.

So many researchers contribute to any dissertation that to name them all compromises the honor of those most involved. More than anyone else, I owe a debt of gratitude to my advisor, Charles Yang, for his commitment to my work and the principle of explanatory adequacy. My other internal committee members, Gene Buckley, Mark Liberman, and Rolf Noyer, and the faculty at IRCS, are responsible for creating an environment at Penn where this (admittedly contentious) dissertation could be written. Though his name appears nowhere else in this document, it is hard to imagine it could exist without the pioneering work of Bill Labov.

The subject of the first chapter was inspired by the mentoring of Jennifer Cole. Important contributions to this dissertation were made by Stephen Anderson, who graciously agreed to serve on my committee, Michael Wagner, who gave me a goal, and Morris Halle, who taught me to never apologize.

I would like to thank my fellow students at Penn, but especially my cohort, Toni Cook, Laurel MacKenzie, and Stefanie Brody. Elsewhere, I have been shown a great deal of kindness by so many, but especially Morgan Sonderregger and Maryam Bakht. Daniel Ezra Johnson fearlessly proofread (\emph{proofreaded}?) the entire document. Among non-linguists, my good friend Carly Fisher stands out for her unflagging support.

>>>>

So many people contributed to this dissertation that to name them all would compromise the honor of the most worthy. 
More than anyone else, I owe a debt of gratitude to my advisor, Charles Yang, whose influence can be seen throughout. 
Gene Buckley, Mark Liberman, and Rolf Noyer, my commitee members, are responsible for creating an environment at Penn where a student could write this admittedly contenious dissertation. 
And though his name appears nowhere else on this document, it is hard to imagine this work could exist without Bill Labov.

My journey in linguistics begins with the mentoring of Jennifer Cole. 
Steve Anderson graciously agreed to serve on my committee. 
Morris Halle told me to never apologize.

I would like to thank my fellow students at Penn, but especially my cohort, Toni Cook, Laurel MacKenzie, and Stefanie Brody. 
Daniel Ezra Johnson fearlessly proofread (\emph{proofreaded}?) the entire document. 
Maryam Bakht kept me centered.

My gratitude also goes out to the administrative assistants at 3401 Walnut and 255 S. 36th, Lauris Olson at the Van Pelt Library, Katherine McEldoon for a helpful review of numerical cognition research, and Carly Fisher for her unflagging support and friendship.
